The Near and Mid-infrared photometric properties of known redshift $z\geq5$ Quasars

### 2019-09-11 tex/MNRAS_submission/rv1/referees_reply.txt

	We thank the Referee for reading our manuscript carefully and for their review and comments.
	We address each of these in turn below (indented text).

	We have also made further, key improvements to our dataset and pipeline.

	We note that after the submission of the original manuscript
	it was brought to our attention (K. Perger; priv. comm) that
	we were missing a 25 confirmed z>5 quasars.  As such, our
	database has increased by 25 objects for a total of 488 VHzQs.

	We also fully re-ran the WFCAM Science Archive (WSA) and VISTA
	Science Archive (VSA) from scratch with the set of updated
	objects. This uncovered a small matching bug for three objects
	in the WSA (no issues were found in the VSA rerun). One of
	these objects, however, is SDSS J2220-0101, which we thought
	had large photometric changes but now acknowledge this was due
	to an incorrect apertureID measurement. The updated photometry
	for SDSS J2220-0101 has the VSA J-band magnitude 19.38+/-0.04
	and a WSA magnitude 19.24+/-0.09.

@@

	Consequently, we have changed the Abstract:
		"Two other quasars, SDSS J0349+0034 and SDSS J2220-0101 had
		significant differences between their WFCAM and VISTA
		magnitudes in one band."
	to
		"Only one quasar, SDSS J0349+0034, shows significant
		differences between WFCAM and VISTA magnitudes in one band."

	We have also added an Appendix to note the update to the overall catalog.

### 2019-09-11 tex/VHzQ.tex
MNRAS_submission/rv1/referees_reply.txt; VHzQ.tex update

\maketitle
\begin{abstract}
We assemble a catalogue of {\bf 488} spectroscopically confirmed very high
($z\geq5.00$) redshift quasars and report their near- ($ZYJHK_{s}/K$)
and mid- (WISE W1234) infrared properties. 97\% of the VH$z$Q sample
is detected in one or more NIR ($ZYJHK/K_{s}$) band, with lack of
coverage rather than lack of depth being the reason for the
non-detections. 362 (78\%) of the very high redshift quasars are
detected at 3.4$\mu$m in the W1 band from the unWISE catalog and all
of the $z\geq7$ quasars are detected in both unWISE W1 and W2. Using
archival WFCAM/UKIRT and VIRCAM/VISTA data we check for photometric
variability that might be expected from super-Eddington accretion. We
find 32 of the quasars have sufficient NIR measurements and
signal-to-noise to look for variability. Weak variability was detected
in multiple bands of SDSS J0959+0227, and very marginally in the
$Y$-band of MMT J0215-0529. Two other quasars, SDSS J0349+0034 and
SDSS J2220-0101 had significant differences between their WFCAM and
VISTA magnitudes in one band.  With supermassive black hole accretion
likely to be redshift invariant up to very high-redshift, further
monitoring of these sources is warranted.  All the data, analysis
codes and plots used and generated here can be found at:
\href{https://github.com/d80b2t/VHzQ}{\tt github.com/d80b2t/VHzQ}.
\end{abstract}

@@

  \subsubsection{Comparing WFCAM and VISTA}
  There are 130 quasars observed in the overlapping area between WFCAM
  and VISTA. We used the {\tt VegaToAB} values to put these objects on
  the same AB system, and for each object compared the two
  measurements. First, we calculated the weighted average (calibrated
  flux) in each filter of both and calculated the ratio and difference
  between each measurement and the average.  Then for each filter we
  calculated the weighted average of the differences (in mag) for each
  instrument to see if there were significant offsets. The results are
  given in Table~\ref{tab:WFCAM_vs_VISTA}.  The only filter with a
  significant offset is the $Y$-band. All of the VISTA averages are
  negative and all of the WFCAM ones are positive. The $Ks$ versus $K$
  band comparison may be affected the different shapes of the filters,
  with $K$ being significantly wider than $K_s$, able to detect light at
  longer wavelengths.
  \begin{table}
    \centering
    \begin{tabular}{l r r}
      \hline  \hline
      abs(VIRCAM & \multirow{2}{*}{millimags} &  no. of  \\
      -  WFCAM)      &                                        &  objects \\
      \hline
      $Z$                 &  23.2 	& 3 \\
      $Y$                 &  57.3 	& 53 \\
      $J$                  &    2.1 	& 106 \\
      $H$                 &  45.8     &  96 \\
      $K_{\rm s}$/$K$ &  25.2     & 110 \\
      \hline  \hline
    \end{tabular}
    \caption{Comparing the magnitudes in different WFCAM/UKIRT and 
      VIRCAM/VISTA near-infrared bands.}
    \label{tab:WFCAM_vs_VISTA}
  \end{table}

  We have also checked for quasars with large differences in magnitude
  between the WSA and VSA. Objects were selected where the average flux
  was $>0.$ and $>5$ average flux error. In order to account for large
  errors in either the WFCAM or VISTA photometry, objects with $\delta$mag$
  < 2 \times$ $\sigma_{\delta\rm mag}$ in either WSA or VSA were removed. This
  selects two quasars with large, $\delta$mag $>0.2$mag differences
  between the WSA and VSA. These are SDSSJ0349+0034 and
  SDSSJ2220-0101. For SDSSJ0349+0034 has a WSA $K$-band magnitude of
  19.13$\pm$0.24, while for the VSA $K_s$-band this is 18.36$\pm$0.10
  mag. For SDSSJ2220-0101, in $J$-band WSA = 22.23$\pm$0.15, for the VSA
  = 19.38$\pm$0.04.

@@

\begin{itemize}
    \item SDSS and Pan-STARRS1 together identified over half of the VH$z$Q sample;  
    \item There remains a quasar ``redshift desert'' at $z\approx5.3-5.7$, though 
      efforts are being made to address this \citep[e.g.,][]{YangJ2018a};
    \item 97.0\% of the VH$z$Q sample is detected in one or more NIR ($ZYJHK/K_{s}$) band; 
    \item The 14 objects that are not detected in the NIR are due to lack of coverage rather than lack of depth; 
   \item 362 (78.2\%) VH$z$Qs are detected by WISE, e.g. in the deeper unWISE W1 catalog. 
 \item All of the $z\geq7$ quasars are detected in both unWISE W1 and W2. 
 \item 32 of the quasars had enough NIR measurements and sufficient NIR measurements and signal-to-noise to look for variability. Weak variability was detected in multiple bands of SDSS J0959+0227, and very marginally in the Y-band of MMT J0215-0529. 2 other quasars, SDSS J0349+0034 and SDSS J2220-0101 had significant differences between their WFCAM and VISTA magnitudes in one band, also indicating variability. 
\end{itemize}

@@

\section{Updated VH$z$Q Sample}
\label{app:qso_sample}
{\bf Between the journal submitted version of this paper (which was
also the arXiv v1) we updated the sample of VH$z$Qs from a total of
463 objects to 488 objects.  16 of these objects were from
\cite{YangJ2018a} and 9 objects were added after discussions with
Krisztina Perger, with the relevant catalog found
\href{http://astro.elte.hu/$\sim$perger/catalog.html}{astro.elte.hu/$\sim$perger/catalog.html}.
We do not include the object DES0141-54 \citep{Belladitta2018}, since we were unable to 
obtain arcsecond level coordinates to perform our matched-aperture photometry.
We also update the positions of five objects, see Table~\ref{tab:disagree_objs}.

>>>>

\maketitle
\begin{abstract}
We assemble a catalogue of {\bf 488} spectroscopically confirmed very high
($z\geq5.00$) redshift quasars and report their near- ($ZYJHK_{s}/K$)
and mid- (WISE W1234) infrared properties. 97\% of the VH$z$Q sample
is detected in one or more NIR ($ZYJHK/K_{s}$) band, with lack of
coverage rather than lack of depth being the reason for the
non-detections. 362 (78\%) of the very high redshift quasars are
detected at 3.4$\mu$m in the W1 band from the unWISE catalog and all
of the $z\geq7$ quasars are detected in both unWISE W1 and W2. Using
archival WFCAM/UKIRT and VIRCAM/VISTA data we check for photometric
variability that might be expected from super-Eddington accretion. We
find 32 of the quasars have sufficient NIR measurements and
signal-to-noise to look for variability. Weak variability was detected
in multiple bands of SDSS J0959+0227, and very marginally in the
$Y$-band of MMT J0215-0529. Only one quasar, SDSS J0349+0034, 
shows significant differences between WFCAM and VISTA magnitudes in one band
With supermassive black hole accretion
likely to be redshift invariant up to very high-redshift, further
monitoring of these sources is warranted.  All the data, analysis
codes and plots used and generated here can be found at:
\href{https://github.com/d80b2t/VHzQ}{\tt github.com/d80b2t/VHzQ}.
\end{abstract}

@@

  \subsubsection{Comparing WFCAM and VISTA}
  There are 131 quasars observed in the overlapping area between WFCAM
  and VISTA. We used the {\tt VegaToAB} values to put these objects on
  the same AB system, and for each object compared the two
  measurements. First, we calculated the weighted average (calibrated
  flux) in each filter of both and calculated the ratio and difference
  between each measurement and the average.  Then for each filter we
  calculated the weighted average of the differences (in mag) for each
  instrument to see if there were significant offsets. The results are
  given in Table~\ref{tab:WFCAM_vs_VISTA}.  The only filter with a
  significant offset is the $Y$-band. All of the VISTA averages are
  negative and all of the WFCAM ones are positive except in the J-band where
  VISTA is marginally positive and WFCAM marginally negative.
  The $Ks$ versus $K$ band comparison may be affected the different shapes of the filters,
  with $K$ being significantly wider than $K_s$, able to detect light at
  longer wavelengths.
  \begin{table}
    \centering
    \begin{tabular}{l r r}
      \hline  \hline
      abs(VIRCAM & \multirow{2}{*}{millimags} &  no. of  \\
      -  WFCAM)      &                                        &  objects \\
      \hline
      $Z$                 &  7.2 	& 3 \\
      $Y$                 &  59.1 	& 62 \\
      $J$                  &    6.3 	& 111 \\
      $H$                 &  41.7     &  103 \\
      $K_{\rm s}$/$K$ &  15.1     & 114 \\
      \hline  \hline
    \end{tabular}
    \caption{Comparing the magnitudes in different WFCAM/UKIRT and 
      VIRCAM/VISTA near-infrared bands.}
    \label{tab:WFCAM_vs_VISTA}
  \end{table}

  We have also checked for quasars with large differences in magnitude
  between the WSA and VSA. Objects were selected where the average flux
  was $>0.$ and $>5$ average flux error. In order to account for large
  errors in either the WFCAM or VISTA photometry, objects with $\delta$mag$
  < 2 \times$ $\sigma_{\delta\rm mag}$ in either WSA or VSA were removed. This
  selects one quasar, SDSS J0349+0034, 
  with large, $\delta$mag $>0.2$mag differences between the WSA and VSA.
  SDSS J0349+0034, has a WSA $K$-band magnitude of 21.03$\pm$0.24
  mag AB, while for the VSA $K_s$-band this is 20.21$\pm$0.10 mag AB.

@@

\begin{itemize}
    \item SDSS and Pan-STARRS1 together identified over half of the VH$z$Q sample;  
    \item There remains a quasar ``redshift desert'' at $z\approx5.3-5.7$, though 
      efforts are being made to address this \citep[e.g.,][]{YangJ2018a};
    \item 97.0\% of the VH$z$Q sample is detected in one or more NIR ($ZYJHK/K_{s}$) band; 
    \item The 14 objects that are not detected in the NIR are due to lack of coverage rather than lack of depth; 
   \item 362 (78.2\%) VH$z$Qs are detected by WISE, e.g. in the deeper unWISE W1 catalog. 
 \item All of the $z\geq7$ quasars are detected in both unWISE W1 and W2. 
 \item 32 of the quasars had enough NIR measurements and sufficient NIR measurements and signal-to-noise to look for variability. Weak variability was detected in multiple bands of SDSS J0959+0227, and very marginally in the Y-band of MMT J0215-0529. SDSS J0349+0034 was the only object to have significant differences between their WFCAM and VISTA magnitudes in one band, potentially indicating variability. 
\end{itemize}

@@

\section{Updated VH$z$Q Sample}
\label{app:qso_sample}
{\bf Between the journal submitted version of this paper (which was
also the arXiv v1) we updated the sample of VH$z$Qs from a total of
463 objects to 488 objects.  16 of these objects were from
\cite{YangJ2018a} and 9 objects were added after discussions with
Krisztina Perger, with the relevant catalog found at 
\href{http://astro.elte.hu/$\sim$perger/catalog.html}{astro.elte.hu/$\sim$perger/catalog.html}.
We do not include the object DES0141-54 \citep{Belladitta2018}, since we were unable to 
obtain arcsecond level coordinates to perform our matched-aperture photometry.
We also update the positions of five objects, see Table~\ref{tab:disagree_objs}.
